\def\CTeXPreproc{Created by ctex v0.2.12, don't edit!}\begin{abstract}
本文中，我们定义了一类新的非自伴代数――~Kadison-Singer 代数，简记为~KS- 代数。此
代数集合了上三角代数，自反代数，von
Neumann 代数的特点。粗略来说，KS- 代数即为相对于其对角子代数的极大上三角自反代数。
许多自伴代数的特性都在~KS- 代数中得以反映。正因如此，定义过程中，我们直接借鉴了~von
Neumann 代数中的一些概念。事实上，KS- 代数的不变子空间格更好的反映了~KS- 代数与~von
Neumann 代数之间的联系。这些自反格是~KS- 代数对角子代数换位子的“极小生成元”。

本文共有三章。在第一章的最后，我们引入了~Kadison-Singer 代数，及~Kadison-Singer 格的定义，
并相对~KS- 代数的对角子代数将其进行了分类。在第二章，我们首先构造了一系列以超有限因子为对角子代数的
~Kadison-Singer 因子，并完全确定了与之相对应的~Kadison-Singer 格，其后我们研究了这些代数的换位子，
最后引入了格不变量用以区分在本章得到的格。在第三章，我们回忆了由两个投影决定的自反代数的
一些性质。接下来描述了由三个自由投影决定的自反格，并证明其为~Kadison-Singer 格，进而得到其决定
的代数为~Kadison-Singer 代数。同时我们证明了此格（除去投影~0，I）同胚于二维球面。
随后我们对于有限~von
Neumann 代数中的投影格引入了一种新的连通关系，并说明任意格在此连通关系下得到的所有连通分支依然构成
格，称其为约化格。其后我们决定了一些已知的格所对应的约化格。最后，我们以对另一类极大上三角性的讨
论结束了全文。\\

{\bf{关键词：}} von
Neumann 代数，超有限，不变子空间，格，自由投影，Kadison-Signer 代数
\end{abstract}



\newpage
\chapter*{Abstract}
In this paper, we defined a new class of non selfadjoint operator
algebras--Kadison-Singer algebras or KS-algebras for simplicity.
These algebras combine triangularity, reflexivity and von Neumann
algebra property into one consideration. Generally speaking,
KS-algebras are reflexive, maximal triangular with respect to its
"diagonal subalgebra". Many selfadjoint features are preserved in
them and concepts can be borrowed directly from the theory of von
Neumann algebras. In fact, a more direct connection of KS-algebras
and von Neumann algebras is through the lattice of invariant
projections of a KS-algebra. The lattice is reflexive and "minimally
generating" in the sense that it generates the commutant of the
diagonal as a von Neumann algebra.

The paper has three chapters. At the end of the first chapter, we
give the definition of Kadison-Singer algebras(as well as
corresponding Kadison-Singer lattices) and a basic classification
according to their diagonals. In chapter 2, we construct
Kadision-Singer factors with hyperfinite factors as their diagonals,
study their commutant and describe the corresponding Kadison-Singer
lattices in details. At the end, a lattice invariant is introduced
to distinguish these lattices. In chapter 3, we first review the
result of reflexive algebras determined by two projections, then
describe the reflexive lattice generated by three free projections
and show that it is a Kadison-Singer lattice and thus the
corresponding algebra is a Kadison-Singer algebra. We also show that
this lattice is homeomorphic to two-dimensional sphere $\S^{2}$(plus
two distinct points corresponding to 0 and I). Then we introduce a
notation of connectedness of projections in a lattice of projections
in a finite von Neumann and show that all connected components form
another lattice, called a reduced lattice. Reduced lattices of most
of our examples were computed. We end this paper by discussing
maximal triangularity in different aspects.

{\bf Keywords:} von Neumann algebras, hyperfinite, invariant space,
lattice, free projection, Kadison-Singer algebras
